
\begin{thebibliography}{}

\bibitem[AlND]{AlND} 聂灵沼, 丁石孙.
\textit{代数学引论（第三版）}. 高等教育出版社, 2021.

\bibitem[AlXX]{AlXX} 徐竞, 徐明曜.
\textit{近世代数初步}. 北京大学出版社, 2020.

\bibitem[AnT1]{AnT1} Terence Tao. \textit{Analysis I} (4th edition). Springer, 2022.

\bibitem[BN]{BN} John H. Conway, Richard K. Guy. \textit{The Book of Numbers}. Springer, 1996.

\bibitem[CAC]{CAC}  Bruce E. Sagan. \textit{Combinatorics: The Art of Counting}. AMS Press, 2020.

\bibitem[CFS]{CFS} Ian Anderson. \textit{Combinatorics of Finite Sets}. Dover, 1987.

\bibitem[CGT]{CGT} David R. Mazur. \textit{Combinatorics: A Guided Tour}. AMS Press, 2010.

\bibitem[CMM]{CMM} Ian Stewart. \textit{Concepts of Modern Mathematics}. Dover, 1995. 

\bibitem[CO]{CO} William J. Cook, William H. Cunningham, William R. Pulleyblank, Alexander Schrijver. \textit{Combinatorial Optimization}. Wiley, 1998.

\bibitem[DMA]{DMA} Kenneth H. Rosen. \textit{Discrete Mathematics and Its Applications} (8th edition). McGraw-Hill, 2019.

\bibitem[EC1]{EC1} Richard P. Stanley. \textit{Enumerative Combinatorics Vol.1} (2nd edition). Cambridge University Press, 2012.

\bibitem[Euclidea]{Euclidea} 
\textit{Euclidea}. https://www.euclidea.xyz/

\bibitem[GI]{GI} Richard E. Schwarz.
\textit{Gallery of the Infinite}. AMS Press, 2016.

\bibitem[GS]{GS} M. A. Armstrong. 
\textit{Groups and Symmetry}. Springer, 1988.

\bibitem[GTS]{GTS} Ian Stewart. 
\textit{Galois Theory} (5th edition). CRC Press, 2023.

\bibitem[IC]{IC} Richard A. Brualdi. 
\textit{Introductory Combinatorics} (5th edition). Pearson, 2009.

\bibitem[ISC]{ISC} 
\textit{Inverse Symbolic Calculator}. https://wayback.cecm.sfu.ca/projects/ISC/ISCmain.html

\bibitem[MaP]{MaP} Peter Winkler. 
\textit{Mathematical Puzzles} (Revised edition). CRC Press, 2024.

\bibitem[MiP]{MiP} Keith J. Devlin. 
\textit{The Millennium Problems: The Seven Greatest Unsolved Mathematical Puzzles of Our Time}. Basic Books, 2002.

\bibitem[NST]{NST} Paul R. Halmos. 
\textit{Naive Set Theory}. Springer, 1974.

\bibitem[OEIS]{OEIS} 
\textit{The On-Line Encyclopedia of Integer Sequences}. https://oeis.org/.

\bibitem[PE]{PE} 
\textit{Project Euler}. https://projecteuler.net/

\bibitem[PFTB]{PFTB}  Martin Aigner, Günter M. Ziegler. \textit{Proofs from THE BOOK}(6th edition). Springer, 2018. 

\bibitem[RBN]{RBN} Richard E. Schwarz.
\textit{Really Big Numbers}. AMS Press, 2014.

\bibitem[RPEC]{RPEC} Joseph H. Silverman, John T. Tate.
\textit{Rational Points on Elliptic Curves} (2nd edition). Springer, 2015.

\bibitem[SMI]{SMI} 单{\CJKfontspec{simsun.ttc}墫}.
\textit{数列与数学归纳法（数学奥林匹克命题人讲座）}. 上海科技教育出版社, 2009.

\end{thebibliography}